Supplementary Information

### 2015-07-01 manuscript/bigtable.tex
Bib files and the rough conversion of my giant table, as submitted July 1 to Proc R Soc

    Alamitos & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,12,25 N & Yes   &       &  \\
    Alford & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,15,41.59 N & Yes   &       &  \\
    Beaver & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,18,58.13 N & Yes   &       &  \\
    Bere  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Woodward2008} & England & stream & 50,45,7 N & Yes   &       &  \\
    Bridge & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,09,42.66 N & Yes   &       &  \\
    Broad & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45.896938 S & Yes   &       &  \\
    Broadstone & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Woodward2005} & stream & stream & 51,01,05 N & Yes   &       &  \\
    Calero & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,11,09 - 20 N & Yes   &       &  \\
    Canton & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) &  \\
    Carpinteria2006 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Lafferty2006} & USA   & estuary & 34.41 - 34.40 N & Yes   &       &  \\
    Chub  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 43,31,39.36 N & Yes   &       &  \\
    Coachella & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Polis1991a} & desert & terrestrial & 33,54 N & Yes   &       &  \\
    Connery & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,18,42.10 N & Yes   &       &  \\
    Corte & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,56,28 - 37,57,39 N & Yes   &       &  \\
    Coyote & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       &  \\
    German & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) &  \\
    GrandeCl & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
    GrandeSc & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
    Guadalupe & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,27,54 - 37,21,17 N & Yes   &       &  \\
    Hainich   & ~\textbackslash{}citet{Riede2011} & Unpublished & Germany & terrestrial &       & No    & Could not locate original source &  \\
    LittleKyeBurn & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) &  \\
    LittleRock & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Martinez1991} & USA   & lake  & 45,44,07.94 N & Yes   &       &  \\
    Mondego & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Patricio2006} & Portugal & estuary & 40,08 N & Yes   &       &  \\
    Montane Forest, Arizona & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Rasmussen1941} & USA   & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) &  \\
    Reef  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Opitz1996} & Caribbean & marine & 18,29 - 17,53 N & Yes   &       &  \\
    Sierra & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Brose2005} & USA   & lake  & 36,50 - 37,02 N & Yes   &       &  \\
    SimberloffE1 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,37.29 N & Yes   &       &  \\
    SimberloffE2 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,33 N & Yes   &       &  \\
    SimberloffE3 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,41,23.82 N & Yes   &       &  \\
    SimberloffE7 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 25,15 N & Yes   &       &  \\
    SimberloffE9 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       &  \\
    SimberloffST2 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,36,16 N & Yes   &       &  \\
    Skipwith & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Warren1989} & England & lake  & 53,40 N & Yes   &       &  \\
    Stink & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 43,37,55.88 N & Yes   &       &  \\
    StMarks & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Christian1999} & USA   & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) &  \\
    Stony  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) &  \\
    TreleaseWoods & ~\textbackslash{}citet{Riede2011} & \multicolumn{1}{l}{~\textbackslash{}citet{Twomey1945}} & USA   & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) &  \\
    Tuesday & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Jonsson2005} & USA   & lake  & 46,13 N & Yes   &       &  \\
    Weddell Sea & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Brose2005} & Antarctica & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) &  \\
    Ythan & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Huxham1996} & UK    & marine &       & No    & Duplicated in Dunne (YthanDunne) &  \\
    BahiaDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Hechinger2011} & Mexico & estuary & 30.43 - 30.46 N & Yes   &       & Parasites removed \\
    CarpinteriaDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Hechinger2011} & USA   & estuary & 34.41 - 34.40 N & Yes   &       & Parasites removed \\
    EsteroDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Hechinger2011} & Mexico & estuary & 31.78 - 31.69 N & Yes   &       & Parasites removed \\
    FjordDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Zander2011} & Germany & estuary & 54.92 - 54.75 N & Yes   &       & Parasites removed \\
    OtagoDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Mouritsen2011} & New Zealand & estuary & 45.78 - 45.88 S & Yes   &       & Parasites removed \\
    SyltDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Thieltges2011} & Denmark & estuary & 54.83 - 55.12 N & Yes   &       & Parasites removed \\
    YthanDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Huxham1996} & Scotland & estuary & 57,18,32 N & Yes   &       & Parasites removed \\
    1     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Qazim1970}} & India & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    2     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Day1967}} & South Africa & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    3     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Woodwell1967}} & USA   & \multicolumn{1}{l}{estuary} & 41,03,11 N & Yes   &       &  \\
    4     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Johnston1956}} & USA   & \multicolumn{1}{l}{estuary} &       & No    & Sink web &  \\
    5     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Teal1962}} & USA   & \multicolumn{1}{l}{estuary} & 31,28,38 N & Yes   &       &  \\
    6     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{MacGinitie1935}} & USA   & \multicolumn{1}{l}{estuary} & 36,48,18 N & Yes   &       &  \\
    7     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kremer1978}} & USA   & \multicolumn{1}{l}{marine} & 41,45 - 41,30 N & Yes   &       &  \\
    8     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Nixon1973}} & USA   & \multicolumn{1}{l}{estuary} & 41,33,00 N & Yes   &       &  \\
    9     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kitching1967}} & Ireland & \multicolumn{1}{l}{stream} &       & No    & Could not locate original source &  \\
    10    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 41 - 47 N & Yes   &       &  \\
    11    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 41 - 47 N & Yes   &       &  \\
    12    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 45,45 - 49 N & Yes   &       &  \\
    13    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 45,45 - 49 N & Yes   &       &  \\
    14    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
    15    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
    16    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Copeland1974}} & USA   & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    17    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hiatt1960}} & Marshall Islands - Pacific Ocean & \multicolumn{1}{l}{marine} & 4,30 - 15 N & No    & Generalized scheme &  \\
    18    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Niering1963a}} & Polynesia & \multicolumn{1}{l}{terrestrial} & 1,01,29 - 1,06,23 N & Yes   &       &  \\
    19    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brooks1963}} & USA   & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
    20    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Knox1970}} & Antarctica & \multicolumn{1}{l}{terrestrial} &       & No    & Could not locate original source &  \\
    21    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Patten1979}} & Antarctica & \multicolumn{1}{l}{marine} & 70-85 S & Yes   &       &  \\
    22    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Summerhayes1923}} & Norway & \multicolumn{1}{l}{terrestrial} & 74,27,54 N & Yes   &       &  \\
    23    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    24    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    25    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    26    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    27    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Varley1970}} & England & \multicolumn{1}{l}{terrestrial} &       & No    & Could not locate original source &  \\
    28    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Paviour-Smith1956}} & New Zealand & \multicolumn{1}{l}{estuary} & 45,51,30 S & Yes   &       &  \\
    29    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dunbar1953}} & Arctic seas & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
    30    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mackintosh1964}} & Antarctica & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
    31    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Petipa1970}} & Black Sea & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
    32    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Petipa1970}} & Black Sea & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
    33    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
    34    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Jones1949}} & UK    & \multicolumn{1}{l}{stream} & 51,41 - 51,55 N & Yes   &       &  \\
    35    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Minshall1967}} & USA   & \multicolumn{1}{l}{stream} & 37,18,26 N & Yes   &       &  \\

>>>>

    Alamitos & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,12,25 N & Yes   &       &  \\
    Alford & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,15,41.59 N & Yes   &       &  \\
    Beaver & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,18,58.13 N & Yes   &       &  \\
    Bere  & ~\citet{Riede2011} & ~\citet{Woodward2008} & England & stream & 50,45,7 N & Yes   &       &  \\
    Bridge & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,09,42.66 N & Yes   &       &  \\
    Broad & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.896938 S & Yes   &       &  \\
    Broadstone & ~\citet{Riede2011} & ~\citet{Woodward2005} & stream & stream & 51,01,05 N & Yes   &       &  \\
    Calero & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,11,09 - 20 N & Yes   &       &  \\
    Canton & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) &  \\
    Carpinteria2006 & ~\citet{Riede2011} & ~\citet{Lafferty2006} & USA   & estuary & 34.41 - 34.40 N & Yes   &       &  \\
    Chub  & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 43,31,39.36 N & Yes   &       &  \\
    Coachella & ~\citet{Riede2011} & ~\citet{Polis1991a} & desert & terrestrial & 33,54 N & Yes   &       &  \\
    Connery & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,18,42.10 N & Yes   &       &  \\
    Corte & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,56,28 - 37,57,39 N & Yes   &       &  \\
    Coyote & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       &  \\
    German & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) &  \\
    GrandeCl & ~\citet{Riede2011} & ~\citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
    GrandeSc & ~\citet{Riede2011} & ~\citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
    Guadalupe & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,27,54 - 37,21,17 N & Yes   &       &  \\
    Hainich   & ~\citet{Riede2011} & Unpublished & Germany & terrestrial &       & No    & Could not locate original source &  \\
    LittleKyeBurn & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) &  \\
    LittleRock & ~\citet{Riede2011} & ~\citet{Martinez1991} & USA   & lake  & 45,44,07.94 N & Yes   &       &  \\
    Mondego & ~\citet{Riede2011} & ~\citet{Patricio2006} & Portugal & estuary & 40,08 N & Yes   &       &  \\
    Montane Forest, Arizona & ~\citet{Riede2011} & ~\citet{Rasmussen1941} & USA   & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) &  \\
    Reef  & ~\citet{Riede2011} & ~\citet{Opitz1996} & Caribbean & marine & 18,29 - 17,53 N & Yes   &       &  \\
    Sierra & ~\citet{Riede2011} & ~\citet{Brose2005} & USA   & lake  & 36,50 - 37,02 N & Yes   &       &  \\
    SimberloffE1 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,37.29 N & Yes   &       &  \\
    SimberloffE2 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,33 N & Yes   &       &  \\
    SimberloffE3 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,41,23.82 N & Yes   &       &  \\
    SimberloffE7 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 25,15 N & Yes   &       &  \\
    SimberloffE9 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       &  \\
    SimberloffST2 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,36,16 N & Yes   &       &  \\
    Skipwith & ~\citet{Riede2011} & ~\citet{Warren1989} & England & lake  & 53,40 N & Yes   &       &  \\
    Stink & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 43,37,55.88 N & Yes   &       &  \\
    StMarks & ~\citet{Riede2011} & ~\citet{Christian1999} & USA   & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) &  \\
    Stony  & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) &  \\
    TreleaseWoods & ~\citet{Riede2011} & \multicolumn{1}{l}{~\citet{Twomey1945}} & USA   & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) &  \\
    Tuesday & ~\citet{Riede2011} & ~\citet{Jonsson2005} & USA   & lake  & 46,13 N & Yes   &       &  \\
    Weddell Sea & ~\citet{Riede2011} & ~\citet{Brose2005} & Antarctica & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) &  \\
    Ythan & ~\citet{Riede2011} & ~\citet{Huxham1996} & UK    & marine &       & No    & Duplicated in Dunne (YthanDunne) &  \\
    BahiaDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & Mexico & estuary & 30.43 - 30.46 N & Yes   &       & Parasites removed \\
    CarpinteriaDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & USA   & estuary & 34.41 - 34.40 N & Yes   &       & Parasites removed \\
    EsteroDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & Mexico & estuary & 31.78 - 31.69 N & Yes   &       & Parasites removed \\
    FjordDunne & ~\citet{Dunne2013} & ~\citet{Zander2011} & Germany & estuary & 54.92 - 54.75 N & Yes   &       & Parasites removed \\
    OtagoDunne & ~\citet{Dunne2013} & ~\citet{Mouritsen2011} & New Zealand & estuary & 45.78 - 45.88 S & Yes   &       & Parasites removed \\
    SyltDunne & ~\citet{Dunne2013} & ~\citet{Thieltges2011} & Denmark & estuary & 54.83 - 55.12 N & Yes   &       & Parasites removed \\
    YthanDunne & ~\citet{Dunne2013} & ~\citet{Huxham1996} & Scotland & estuary & 57,18,32 N & Yes   &       & Parasites removed \\
    1     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Qazim1970}} & India & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    2     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Day1967}} & South Africa & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    3     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Woodwell1967}} & USA   & \multicolumn{1}{l}{estuary} & 41,03,11 N & Yes   &       &  \\
    4     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Johnston1956}} & USA   & \multicolumn{1}{l}{estuary} &       & No    & Sink web &  \\
    5     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Teal1962}} & USA   & \multicolumn{1}{l}{estuary} & 31,28,38 N & Yes   &       &  \\
    6     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{MacGinitie1935}} & USA   & \multicolumn{1}{l}{estuary} & 36,48,18 N & Yes   &       &  \\
    7     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kremer1978}} & USA   & \multicolumn{1}{l}{marine} & 41,45 - 41,30 N & Yes   &       &  \\
    8     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Nixon1973}} & USA   & \multicolumn{1}{l}{estuary} & 41,33,00 N & Yes   &       &  \\
    9     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kitching1967}} & Ireland & \multicolumn{1}{l}{stream} &       & No    & Could not locate original source &  \\
    10    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 41 - 47 N & Yes   &       &  \\
    11    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 41 - 47 N & Yes   &       &  \\
    12    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 45,45 - 49 N & Yes   &       &  \\
    13    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 45,45 - 49 N & Yes   &       &  \\
    14    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
    15    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
    16    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Copeland1974}} & USA   & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    17    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hiatt1960}} & Marshall Islands - Pacific Ocean & \multicolumn{1}{l}{marine} & 4,30 - 15 N & No    & Generalized scheme &  \\
    18    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Niering1963a}} & Polynesia & \multicolumn{1}{l}{terrestrial} & 1,01,29 - 1,06,23 N & Yes   &       &  \\
    19    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Brooks1963}} & USA   & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
    20    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Knox1970}} & Antarctica & \multicolumn{1}{l}{terrestrial} &       & No    & Could not locate original source &  \\
    21    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Patten1979}} & Antarctica & \multicolumn{1}{l}{marine} & 70-85 S & Yes   &       &  \\
    22    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Summerhayes1923}} & Norway & \multicolumn{1}{l}{terrestrial} & 74,27,54 N & Yes   &       &  \\
    23    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    24    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    25    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    26    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    27    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Varley1970}} & England & \multicolumn{1}{l}{terrestrial} &       & No    & Could not locate original source &  \\
    28    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Paviour-Smith1956}} & New Zealand & \multicolumn{1}{l}{estuary} & 45,51,30 S & Yes   &       &  \\
    29    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Dunbar1953}} & Arctic seas & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
    30    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Mackintosh1964}} & Antarctica & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
    31    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Petipa1970}} & Black Sea & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
    32    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Petipa1970}} & Black Sea & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
    33    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
    34    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Jones1949}} & UK    & \multicolumn{1}{l}{stream} & 51,41 - 51,55 N & Yes   &       &  \\
    35    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Minshall1967}} & USA   & \multicolumn{1}{l}{stream} & 37,18,26 N & Yes   &       &  \\
    36    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
    37    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Clarke1967}} & USA   & \multicolumn{1}{l}{marine} & 41,02,49 N & Yes   &       &  \\
    38    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
    39    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
    40    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Harrison1962}} & Malaysia & \multicolumn{1}{l}{terrestrial} &       & No    & Generalized scheme &  \\
    41    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Parin1970}} & Israel & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
    42    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Vinogradov1978}} & Pacific Ocean & \multicolumn{1}{l}{marine} &       & No    & Study site unclear &  \\
    43    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Rosenthal1974}} & USA   & \multicolumn{1}{l}{marine} & 32,57 N & Yes   &       &  \\
    44    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Yanez1978}} & Mexico & \multicolumn{1}{l}{marine} & 17,26,21 N & Yes   &       &  \\
    45    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Tilly1968}} & USA   & \multicolumn{1}{l}{stream} & 41,22,55 N & Yes   &       &  \\
    46    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Patten1975}} & USA   & \multicolumn{1}{l}{lake} & 33,54 N & Yes   &       &  \\
    47    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Harris1980}} & USA   & \multicolumn{1}{l}{lake} &       & No    & Study site unclear &  \\
    48    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Simenstad1978}} & USA   & \multicolumn{1}{l}{marine} &       & No    & Extinct species &  \\
